Writing a reproducible paper with R Markdown and Pagedown^[Corresponding adress: mail@paulcbauer.eu, camille.landesvatter@mzes.uni-mannheim.de]

### 2022-01-28 paper.Rmd
Use gt for regression table.

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install the "pagedown"-package from github using the code below [@Xie2021-bi; @Xie2021-ls].
```{r eval=FALSE, include=TRUE}
remotes::install_github('rstudio/pagedown')
```
* ...also install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "modelsummary", "knitr"))
```
* ...download the 4 input files we created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1rWzj-Bu1EKqkSuE1gaFzduBJhzlThpkw?usp=sharing). Ignore the other files.
* ...also download the 4 styling files we created: `wp_paged.html`, `wp.css`, `wp-fonts.css` and `wp-pages.css`.
* ...store all 8 files from above together in one folder (and use this folder as your working directory later on)
* ...learn R and read about the other underlying components namely [Markdown](https://en.wikipedia.org/wiki/Markdown), [R Markdown](https://rmarkdown.rstudio.com/lesson-1.html) and [Pagedown](https://pagedown.rbind.io/).
* ...pagedown comes with several Rmd-templates (presentations, poster, thesis, etc.) and via this review we provide another template for a working paper style. If however you want to modify single aspects or create your own template, you will need to at least gain some basic skills in [CSS](https://www.w3schools.com/css/) and [HTML](https://www.w3schools.com/html/).

@@

Table \@ref(tab:table-5) shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.

@@

tab_reg <-modelsummary(models, title = 'A regression table.', output = 'flextable')

# additionally we want to change the font, font size and spacing
library("gdtools")

tab_reg <- tab_reg %>%
  font(fontname="Times New Roman", part="header") %>%
  font(fontname="Times New Roman", j=1:4) %>% 
  fontsize(size=10, part="header") %>%
  fontsize(size=10, j=1:4) %>% 
  line_spacing(space = 0.3, part = "all")

tab_reg

>>>>

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install the "pagedown"-package from github using the code below [@Xie2021-bi; @Xie2021-ls].
```{r eval=FALSE, include=TRUE}
remotes::install_github('rstudio/pagedown')
```
* ...also install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "modelsummary", "knitr", "gt"))
```
* ...download the 4 input files we created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1rWzj-Bu1EKqkSuE1gaFzduBJhzlThpkw?usp=sharing). Ignore the other files.
* ...also download the 4 styling files we created: `wp_paged.html`, `wp.css`, `wp-fonts.css` and `wp-pages.css`.
* ...store all 8 files from above together in one folder (and use this folder as your working directory later on)
* ...learn R and read about the other underlying components namely [Markdown](https://en.wikipedia.org/wiki/Markdown), [R Markdown](https://rmarkdown.rstudio.com/lesson-1.html) and [Pagedown](https://pagedown.rbind.io/).
* ...pagedown comes with several Rmd-templates (presentations, poster, thesis, etc.) and via this review we provide another template for a working paper style. If however you want to modify single aspects or create your own template, you will need to at least gain some basic skills in [CSS](https://www.w3schools.com/css/) and [HTML](https://www.w3schools.com/html/).

@@

Table \@ref(tab:table-5) shows the output for a regression table. Make sure you name all the models you estimate (even if its 50) and explicitly refer to model names (M1, M2 etc.) in the text.

@@

library(gt)
# additionally we want to change the font, font size and spacing
modelsummary(models,
             title = 'Linear regression',
             output = 'gt',
             notes = "Notes: some notes...") %>%
    tab_spanner(label = 'Dependent variable: Fertility', columns = 2:4) %>%
  tab_options(
    table.font.size = 10,
    data_row.padding = px(1),
    table.border.top.color = "white",
    heading.border.bottom.color = "black",
    row_group.border.top.color = "black",
    row_group.border.bottom.color = "white",
    table.border.bottom.color = "white",
    column_labels.border.top.color = "black",
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.color = "black",
    table_body.hlines.color = "white"
  )
